\paperTitle

### 2014-05-17 doc/icml2014/intro.tex

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{
  Overview of our approach:
  we first use tensor factorization to learn the \emph{conditional moments}
  for each hidden variable.
  Second, we optimize a composite marginal likelihood to recover the \emph{hidden clique marginals},
  from which we solve for the \emph{model parameters}.
  }
\end{figure}

>>>>

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{
  Overview of our approach:
  (i) we use tensor factorization to learn the \emph{conditional moments}
  for each hidden variable;
  (ii) we optimize a composite likelihood to recover the hidden \emph{marginals};
  and (iii) we optimize another likelihood objective to the \emph{model parameters}.
  Both likelihood objectives are convex.
  }
\end{figure}
